**The status of the microbial census: an update**

### 2016-01-18 doc/notebook/Bacterial_data_acquisition.Rmd
Bring in EMIRGE metadata

XXXXXXXXXX

@@

#these sequences are missing from fasta file
#metadata_genome_id[! metadata_genome_id %in% names(seq_numbers)]
#probably not a horrible thing since not all genomes could give a 16S rRNA gene
#sequence

@@

@@

>>>>

@@

# these sequences are missing from fasta file
# metadata_genome_id[! metadata_genome_id %in% names(seq_numbers)]
# probably not a horrible thing since not all genomes could give a 16S rRNA gene
# sequence
#
# [1] "SCGC AAA015-N04" "SCGC AAA536-N21" "SCGC AAA158-B04" "SCGC AAA036F23"
# [5] "SCGC AAA001-B15" "SCGC AAA164-N20" "SCGC AAA536-J20" "SCGC AAA008-P15"
# [9] "SCGC AAA536-G18" "SCGC AAA001-B15"

@@

We'd also like to get the metadata from the EMIRGE data. We have an metadata file was created above with `code/get_emirge.metadata.sh` that we'll read in and concatenate to the end of `bacteria.good.metadata`.

```{r emirge_metadata}
emirge_metadata <- read.table(file="data/raw/emirge.metadata", row.names=1)
bacteria_sequences <- read.table(file="data/mothur/emirge.bacteria.taxonomy", stringsAsFactors=FALSE)[1]
bacteria_emirge_metadata <- emirge_metadata[bacteria_sequences$V1,]

write.table(bacteria_emirge_metadata, file="data/mothur/bacteria.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)
```

@@

table(metadata$category)

#    AE    AQB   AQBS    AQF   AQFS    AQH    AQI    AQM   AQMS    AQO     BD
#  3473   1094    390  59220  23979  10861   2073 134788  27811   8765  33152
#    BF     BI     BO     BP     OT     PO     PR     PS     SA     SD     SO
# 11813  16598   8556  38710  19417   9753  19695   4892  10051   3059  60335
#    SP     ZA     ZN     ZO     ZV
#  1922  13209   7476  10855 794492
